Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Updating paper based on new bug discovery.
related work

\section{Background}
TODO(SAM):
\subsection{Related Work}

>>>>

\section{Background}
\subsection{Related Work}
Concept extraction in medicine is an increasingly well-studied problem. One of the main driving forces behind such research is the annual i2b2/VA Workshop on Natural Language Processing Challenges for Clinical Records, which challenges participants to develop a system for "the extraction of medical concepts from patient reports." Torii et al. \cite{torii}, for example, developed a system using the same training data as us for the workshop. Their concept extraction system was trained using a tagger specifically developed for the biology domain, and their work shows the difficulty in porting trained systems across clinical documents from various sources.

In a work independent of the i2b2 workshop, Meystre and Haug \cite{meystre} developed a system for automatically retrieve medical problems from free-form text. Their system addresses one of the labels extracted from our system and references a pre-defined Problem List rather than training on data that is presumed to be a subset of possible terms. Tackling an interesting related problem, Happe et al. \cite{heppe} present a system for automatic concept extraction from $spoken$ medical reports in French, with robust performance in testing in spite of sensitivities to ambiguous pronunciations and acronyms, which are common in automatic speech recognition systems.
